{mscstexta4r}

### 2016-06-21 README.Rmd
Document that topic detection is English only

This API returns the detected topics for a list of submitted text records. A
topic is identified with a key phrase, which can be one or more related words.
This API requires a minimum of 100 text records to be submitted, but is designed
to detect topics across hundreds to thousands of records. The API is designed to
work well for short, human-written text such as reviews and user feedback.

@@

```{r eval = FALSE}
# Detect top topics in group of documents
textaDetectTopics(
  documents,                  # At least 100 documents
  stopWords = NULL,           # Stop word list (optional)
  topicsToExclude = NULL,     # Topics to exclude (optional)
  minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)
  maxDocumentsPerWord = NULL, # Threshold to exclude ubiquitous topics (optional)
  resultsPollInterval = 30L,  # Poll interval (in s, default: 30s, use 0L for async)
  resultsTimeout = 1200L,     # Give up timeout (in s, default: 1200s = 20mn)
  verbose = FALSE             # If set to TRUE, print every poll status to stdout
)
```

@@

  # Detect top topics
  textaDetectTopics(
    documents = yelpChReviews100, # At least 100 docs/sentences
    stopWords = NULL,             # Stop word list (optional)
    topicsToExclude = NULL,       # Topics to exclude (optional)
    minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
    maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
    resultsPollInterval = 30L,    # Poll interval (in s, default: 30s, use 0L for async)
    resultsTimeout = 1200L,       # Give up timeout (in s, default: 1200s = 20mn)
    verbose = FALSE               # If set to TRUE, print every poll status to stdout
  )

@@

  # Detect top topics
  operation <- textaDetectTopics(
    documents = yelpChReviews100, # At least 100 docs/sentences
    resultsPollInterval = 0L      # Poll interval (in s, default: 30s, use 0L for async)
  )

>>>>

This API returns the detected topics for a list of submitted text records. A
topic is identified with a key phrase, which can be one or more related words.
This API requires a minimum of 100 text records to be submitted, but is designed
to detect topics across hundreds to thousands of records. The API is designed to
work well for short, human-written text such as reviews and user feedback.
English is the only language supported at this time.

@@

```{r eval = FALSE}
# Detect top topics in group of documents
textaDetectTopics(
  documents,                  # At least 100 documents (English only)
  stopWords = NULL,           # Stop word list (optional)
  topicsToExclude = NULL,     # Topics to exclude (optional)
  minDocumentsPerWord = NULL, # Threshold to exclude rare topics (optional)
  maxDocumentsPerWord = NULL, # Threshold to exclude ubiquitous topics (optional)
  resultsPollInterval = 30L,  # Poll interval (in s, default: 30s, use 0L for async)
  resultsTimeout = 1200L,     # Give up timeout (in s, default: 1200s = 20mn)
  verbose = FALSE             # If set to TRUE, print every poll status to stdout
)
```

@@

  # Detect top topics
  textaDetectTopics(
    documents = yelpChReviews100, # At least 100 docs/sentences (English only)
    stopWords = NULL,             # Stop word list (optional)
    topicsToExclude = NULL,       # Topics to exclude (optional)
    minDocumentsPerWord = NULL,   # Threshold to exclude rare topics (optional)
    maxDocumentsPerWord = NULL,   # Threshold to exclude ubiquitous topics (optional)
    resultsPollInterval = 30L,    # Poll interval (in s, default: 30s, use 0L for async)
    resultsTimeout = 1200L,       # Give up timeout (in s, default: 1200s = 20mn)
    verbose = FALSE               # If set to TRUE, print every poll status to stdout
  )

@@

  # Detect top topics
  operation <- textaDetectTopics(
    documents = yelpChReviews100, # At least 100 docs/sentences (English only)
    resultsPollInterval = 0L      # Poll interval (in s, default: 30s, use 0L for async)
  )
